%!TEX root = main.tex

\



\section{Track Record}

\subsection{Prof. Steven Murdoch}

Steven Murdoch is Professor of Security Engineering at University College London and is the head of the Information Security Research Group. 

Professor Murdoch has worked extensively in payment system security, including fraud prevention and consumer protection.
His proposed security measures have been adopted in the EMV protocol, now the most widely used smart card payment system worldwide.
He also led the commercialisation of a new authentication scheme for online banking that is used by the largest banks in Europe (including Commerzbank, Deutschebank and Rabobank).
This system was acquired by OneSpan, a leading provider of authentication products in the financial industry.

His work on protecting vulnerable banking customers from unfair treatment has guided the development of the current consumer protection scheme against push payment fraud, and he is currently working on how this should be revised based on experience of this being in use.

Professor Murdoch is also closely involved in the relationship between computer science and the law, and is regularly an expert witness in disputes over fraudulent payments.
He is the author of ``The sources and characteristics of electronic evidence and artificial intelligence'' (\href{https://humanities-digital-library.org/index.php/hdl/catalog/book/electronic-evidence-and-electronic-signatures}{[\x]}) and is leading the writing team on a Royal Society
project to provide guidance to the judiciary on the interpretation of electronic evidence in court.

In the field of anonymous communications, Professor Murdoch has developed both theoretical and practical breakthroughs in privacy enhancing technologies.
He has applied game-theory to the design of censorship-resistance schemes and the results have been adopted by the Tor Project.
He was also the creator of Tor Browser, the primary means for users to access the Tor anonymous communication network.

In the last five years he has published at top-tier publication venues in the field of information security and payment systems including Financial Cryptography, ESORICS, ASIACCS, and ACM SIGCOMM CCR. He is a fellow of the BCS and IET and a Royal Society University Research Fellow, a member of the advisory board for the Foundation for Information Policy Research and is a director of the Open Rights Group.

\subsection{Dr Aydin Abadi}


Aydin Abadi is a Senior Research Fellow at UCL’s Department of Computer Science.  He also held a Lectureship position at the University of Gloucestershire and before that he was a Research Associate at the Blockchain Technology Lab, at the University of Edinburgh. His primary research interests include cryptography and cryptocurrency, with a focus on (a) payment fraud, (b) developing Privacy Enhancing Technologies (PETs), (c) blockchain technology, and (d) cloud computing. Since 2017, when he received his PhD, in Private Set Intersection (PSI), he has been leading the development and implementation of various cryptographic protocols. 

The privacy-preserving techniques he pioneered have become staples in the field of PSI, see \href{https://link.springer.com/chapter/10.1007/978-3-319-18467-8_1}{[\x]} and \href{https://link.springer.com/chapter/10.1007/978-3-662-54970-4_9}{[\x]}. He designed the first delegated PSI that lets data storage and private computation be outsourced to powerful but potentially malicious cloud computing. To date, the updatable PSI that he discovered remains the only PSI supporting data updates with low communication and computation costs \href{https://link.springer.com/chapter/10.1007/978-3-031-18283-9_6}{[\x]}.  


He has also contributed to the (theoretical) security of online banking to help honest victims of online banking fraud prove their innocence, and receive compensation for their financial losses, see \href{https://eprint.iacr.org/2022/107.pdf}{[\x]}. He has several publications in the field of blockchain technology and cryptocurrency as well; for instance, he designed a generic fair exchange protocol that lets users securely pay in cryptocurrency for any verifiable digital services if and only if they receive the promised services; his proposed protocol can preserve users' privacy and can prevent fraud in the case where either a malicious service provider wants to receive payment without delivering the service, see \href{https://arxiv.org/pdf/2208.00283.pdf}{[\x]}. He has developed two decentralised (i.e., blockchain-based) platforms that are still functional and online (see \href{http://blockchainlab.inf.ed.ac.uk/id-management/#/}{[\x]} and \href{http://blockchainlab.inf.ed.ac.uk/valued/}{[\x]} for more details).


Recently, he as part of a team (consisting of Prof. Steven Murdoch and a company called Privitar) won the first phase of the “UK-US Privacy Enhancing Technologies Challenge Prize” resulting in attracting £60k in funding, see \href{https://www.ucl.ac.uk/computer-science/news/2022/dec/ucl-computer-sciences-success-privacy-enhancing-technologies-challenge}{[\x]}.  He has over 20 technical papers and 6 open-source prototypes in the field of cryptography and cryptocurrency. Five of his papers are at CORE “A” ranked conferences and journals.


\subsection{Host Institution}
UCL has one of the world's leading computer science (CS) departments, which has been recognised as an “Academic Centre of Excellence in Cyber Security Research”. Both PI and Co-I are members of UCL Information Security Research Group (ISec) which hosts top-tier researchers some of whom have research interests strongly aligned with the proposed research programme; for instance, Sarah Meiklejohn  (in blockchain technology), Philipp Jovanovic (in cryptography), and Lorenzo Cavallaro (systems security). 


\subsection{Partners}



\input{refer-2}

